### 2013-06-04 trunk/papers/bprheo_r/bprheo.tex
Moving revision into place
git-svn-id: https://ccpforge.cse.rl.ac.uk/svn/ludwig@1995 40876441-3496-0410-a613-a2fca35b2ae2

@@

%If the flow rate exceeds a certain critical value BPII does not undergo the 
%homogeneous deformation described above and adopts another mode of flow. 
%Fig. \ref{bp2-high} shows a sequence of cuts through the director 
%field at high shear rate. The entire blue phase network has broken up 
%into a simple cholesteric helix and flows as a travelling 
%helical wave with the helical axis oriented along the vorticity direction.
%The state is translationally invariant in the flow and gradient directions.
%It is the preferred mode of flow of a standard cholesteric phase
%in vorticity mode at low Ericksen numbers. This is followed by
%the uncoiling transition to a nematic, flow-aligned state at even 
%higher shear rates ~\cite{Rey:1996a, Rey:1996b}.

%In our scenario the BP to cholesteric transition occurs for shear rates $\gd\simeq 4.68\e{-4}$, which
%corresponds to Ericksen numbers of ${\it Er}\simeq4$, based on our
%parameters for BPII ($K=0.02, \eta=0.666$, and $p_0/2=16$;
%see Table \ref{tab1} in the Appendix).

%\begin{figure}[htpb]
%\includegraphics[width=0.495\textwidth]{dir+y-250k_run949.png}
%\includegraphics[width=0.495\textwidth]{dir+y-253k_run949.png}
%\includegraphics[width=0.495\textwidth]{dir+y-255k_run949.png}
%\includegraphics[width=0.495\textwidth]{dir+y-257k_run949.png}
%\caption{Director field of BPII at high shear rate: The images show snapshots at time steps 
%$t=2.50, 2.53,2.55, 2.57\e{5}$ (from top to bottom) with flow into/out of the page. The colour code gives the alignment of the director field in the flow direction (x) with red fully aligned and blue out of plane. 
%The configuration is a helical wave that travels along the direction of vorticity.
%It is translationally invariant along the gradient and flow direction.}
%\label{bp2-high}
%\end{figure}

@@

\if{The negative branch in the shear stress is connected
to a local maximum followed by a local minimum in the 
average free energy. Hence, the region of negative stress can be 
regarded as a phase during which elastic forces exert a 
'pull' on the network while it tries to reach a more 
favourable configuration. However, the low flow rate
causes this unstable intermediate state to be exposed to these
elastic forces for a relatively long time, long enough to 
create small distortions which finally break the symmetry of the
flow-induced configuration.}\fi

@@

At high flow rates, $6.25\e{-4}\lesssim\gd\lesssim7.81\e{-4}$ ($10.67\lesssim {\it Er}\lesssim 13.33$), 
we observe a break-up of the flow-induced 
disclination network of regime BPI-2. However, 
in contrast to BPII, where the configuration is a travelling helical 
wave (cf. Fig. \ref{bp2-high}), BPI breaks down into a quasi 
two-dimensional, translationally invariant state, which is shown in 
Fig. \ref{bp1-high}. 
There are distinctive regions where the director field is 
predominantly oriented along the vorticity direction and 
other regions where it is oriented rather in flow-gradient plane. 
Occasionally, while moving past each other, these rolls resemble 
regions of local double twist.
Interestingly the critical Ericksen number for the break-up lies in 
about the same window as that of transition between BPII-1 and BPII-2.

%\begin{figure}[htpb]
%\includegraphics[width=0.45\textwidth]{dir3d-z-302k_run916.png}
%\caption{Director field of BPI at high shear rate: The pictures show a region 
%of $L_x\times L_y \times L_z= 32^3$ lattice sites with the flow/gradient 
%direction oriented along the horizontal/vertical axis. 
%The colour code gives the magnitude of the z-component of the director field. 
%The data show that the structure is quasi-2D, with rolling double twist
%patterns in the $xy$ plane, and an approximate translational symmetry 
%along the vorticity direction.}
%\label{bp1-high}
%\end{figure}

@@

BPII  & & & & $\times 10^5$ \\
\hline
BPII-1 &0.24 &0.02 & 0.1963 & & & & & & & & & \\
BPII-1 &0.49 &0.04 & 0.1963 & & & & & & & & & \\
BPII-1 &0.98 &0.08 & 0.1963 & & & & & & & & & \\
BPII-1 &1.95 &0.17 & 0.1963 & & & & & & & & & \\
BPII-1 &3.91 &0.33 & 0.1963 & & & & & & & & & \\
BPII-1 &7.81 &0.67 & 0.1963 & & & & & & & & & \\
BPII-1 &15.63 &1.33 & 0.1963 & & & & & & & & & \\
BPII-1 &15.63 &1.33 & -0.1963 & & & & & & & & & \\
BPII-1 &31.25 &2.66 & 0.1963 & & & & & & & & & \\
BPII-1 &39.06 &3.33 & 0.1963 & & & & & & & & & \\
%BPII-1 & 0.244 &0.02 & 0.1963 &-7.75 &7.70 &0.13 &-0.17 &0.17 &0.13 &-0.24 &0.23 &0.19 \\
%BPII-1 & 0.488 &0.04 & 0.1963 &-15.50 &15.40 &0.19 &-0.32 &0.30 &0.21 &-0.43 &0.42 &0.29 \\
%BPII-1 & 0.976 &0.08 & 0.1963 &-31.01 &30.80 &0.33 &-0.60 &0.58 &0.41 &-0.85 &0.79 &0.47 \\
%BPII-1 & 1.95 &0.17  & 0.1963 &-62.04  &61.60 & 0.97 & -1.09 &1.07 & 0.76 & -1.64 & 1.55 & 0.81\\
%BPII-1 &3.91 & 0.33& 0.1963 &-123.93 &123.18 & 1.76 &-1.66 &1.70 & 1.45 &-3.09& 2.73 &1.47\\
%BPII-1 &7.81 &0.67 & 0.1963  &-247.67 &246.45 & 3.20 &-2.62 &2.71 & 2.67 &-5.78 & 4.77 &2.74\\
%BPII-1 &15.63 & 1.33& 0.1963 &-494.85 &493.09 & 5.64 &-3.13 &3.31 &4.24 &\bf{-10.00} & \bf{7.66} &4.33\\
%BPII-1 & 15.63 & 1.33& -0.1963&-494.85 &493.09 & 5.64 & -3.13 &3.31 &4.24 &\bf{-7.66} & \bf{10.00} &4.33\\
%BPII-1 & 31.25 &2.67 & 0.1963 &-988.73 &985.93 &8.96  &-1.79 &1.82 &5.86 &-14.39 & 11.04 &6.35\\
\hline
GJT (BPII-2)&46.87 &4.00 & 0.1963 & & & & & & & & & \\
GJT (BPII-2)&54.69 &4.67 & 0.1963 & & & & & & & & & \\
GJT (BPII-2)&62.5 &5.33 & 0.1963 & & & & & & & & & \\
GJT (BPII-2)&78.13 &6.01 & 0.1963 & & & & & & & & & \\
GJT (BPII-2)&93.75 &8.00 & 0.1963 & & & & & & & & & \\
GJT (BPII-2)&125.0 &10.66 & 0.1963 & & & & & & & & & \\
%GJT (BPII-2)& 62.50 & 5.34& 0.1963 & -1969.41  & 1969.41 & 3.07 & -1.20 & 1.20 & 0.38 &-0.96 & 1.48 &0.38 \\
%GJT (BPII-2) & 78.13 & 6.66 &  0.1388 &-2458.60 & 2458.61  &0.37 &- &- &- &-18.54 &16.94 &0.32 \\
%GJT (BPII-2)& 93.75 &8.00 & 0.1388 &-2950.2  &2950.2 &0.50 &- &- &- &-22.69 & 19.72 & 0.04\\
\hline
FAN &187.5 &16.00 & 0.1963 &  & & &  &  &  & & & \\
FAN &250.0 &21.33 & 0.1963 &  & & &  &  &  & & & \\
%FAN & 125.0 &10.67 & 0.1388 &-3937.31  & 3937.32 &0.28 &-  &-  &-  &-1.79 &1.15  &0.14 \\
\hline
\end{tabular}
\caption{Minima, maxima and standard deviation of time-averaged velocity components 
for BPI ($\tau=-0.5, \kappa=1.0$) and BPII ($\tau=-0.5, \kappa=2.0$) in steady 
shear flow. All velocity values are given in $10^{-5}$ lattice units. The transient dynamics 
has not been included in the averages. The regimes comprise the formation
of an amorphous network (BPI-1), periodically recurring conformations (BPI-2 and BPII-1), 
two-dimensional double twist rolls (BPI-3), a one-dimensional travelling helical wave (BPII-2), 
a cholesteric helix oriented along the gradient direction (CHG), 
and a flow-aligned nematic state (FAN).
(Last six columns refer to the secondary flow.)}
\label{tab1}
\end{table*}

>>>>

\newif\ifold
%\oldtrue

@@

% New conformation is presumably metastable %
\ifold{If the flow rate exceeds a certain critical value BPII does not undergo the 
homogeneous deformation described above and adopts another mode of flow. 
Fig. \ref{bp2-high} shows a sequence of cuts through the director 
field at high shear rate. The entire blue phase network has broken up 
into a simple cholesteric helix and flows as a travelling 
helical wave with the helical axis oriented along the vorticity direction.
The state is translationally invariant in the flow and gradient directions.
It is the preferred mode of flow of a standard cholesteric phase
in vorticity mode at low Ericksen numbers. This is followed by
the uncoiling transition to a nematic, flow-aligned state at even 
higher shear rates ~\cite{Rey:1996a, Rey:1996b}.

In our scenario the BP to cholesteric transition occurs for shear rates $\gd\simeq 4.68\e{-4}$, which
corresponds to Ericksen numbers of ${\it Er}\simeq4$, based on our
parameters for BPII ($K=0.02, \eta=0.666$, and $p_0/2=16$;
see Table \ref{tab1} in the Appendix).

\begin{figure}[htpb]
%\includegraphics[width=0.495\textwidth]{dir+y-250k_run949.png}
%\includegraphics[width=0.495\textwidth]{dir+y-253k_run949.png}
%\includegraphics[width=0.495\textwidth]{dir+y-255k_run949.png}
%\includegraphics[width=0.495\textwidth]{dir+y-257k_run949.png}
\caption{Director field of BPII at high shear rate: The images show snapshots at time steps 
$t=2.50, 2.53,2.55, 2.57\e{5}$ (from top to bottom) with flow into/out of the page. The colour code gives the alignment of the director field in the flow direction (x) with red fully aligned and blue out of plane. 
The configuration is a helical wave that travels along the direction of vorticity.
It is translationally invariant along the gradient and flow direction.}
\label{bp2-high}
\end{figure}
\fi

@@

\ifold{The negative branch in the shear stress is connected
to a local maximum followed by a local minimum in the 
average free energy. Hence, the region of negative stress can be 
regarded as a phase during which elastic forces exert a 
'pull' on the network while it tries to reach a more 
favourable configuration. However, the low flow rate
causes this unstable intermediate state to be exposed to these
elastic forces for a relatively long time, long enough to 
create small distortions which finally break the symmetry of the
flow-induced configuration.}\fi

@@

\ifold At high flow rates, $6.25\e{-4}\lesssim\gd\lesssim7.81\e{-4}$ ($10.67\lesssim {\it Er}\lesssim 13.33$), 
we observe a break-up of the flow-induced 
disclination network of regime BPI-2. However, 
in contrast to BPII, where the configuration is a travelling helical 
wave (cf. Fig. \ref{bp2-high}), BPI breaks down into a quasi 
two-dimensional, translationally invariant state, which is shown in 
Fig. \ref{bp1-high}. 
There are distinctive regions where the director field is 
predominantly oriented along the vorticity direction and 
other regions where it is oriented rather in flow-gradient plane. 
Occasionally, while moving past each other, these rolls resemble 
regions of local double twist.
Interestingly the critical Ericksen number for the break-up lies in 
about the same window as that of transition between BPII-1 and BPII-2.

\begin{figure}[htpb]
%\includegraphics[width=0.45\textwidth]{dir3d-z-302k_run916.png}
\caption{Director field of BPI at high shear rate: The pictures show a region 
of $L_x\times L_y \times L_z= 32^3$ lattice sites with the flow/gradient 
direction oriented along the horizontal/vertical axis. 
The colour code gives the magnitude of the z-component of the director field. 
The data show that the structure is quasi-2D, with rolling double twist
patterns in the $xy$ plane, and an approximate translational symmetry 
along the vorticity direction.}
\label{bp1-high}
\end{figure}
\fi

@@

BPII  & & & & $\times 10^5$ \\
\hline
BPII-1 &0.24 &0.02 & 0.1963 &-7.8 &7.7 &0.1 &-0.2 &0.2 &0.1 &-0.3 &0.3 &0.2 \\
BPII-1 &0.49 &0.04 & 0.1963 &-15.5 &15.4 &0.2 &-0.3 &0.4 &0.2 &-0.5 &0.4 &0.2 \\
BPII-1 &0.98 &0.08 & 0.1963 &-31.0 &30.8 &0.3 &-0.6 &0.6 &0.4 &-0.9 &0.8 &0.4 \\
BPII-1 &1.95 &0.17 & 0.1963 &-62.0 &61.6 &0.6 &-1.2 &1.2 &0.8 &-1.8 &1.6 &0.8 \\
BPII-1 &3.91 &0.33 & 0.1963 &-123.9 &123.3 &1.2 &-2.1 &2.1 &1.6 &-3.4 &3.0 &1.5 \\
BPII-1 &7.81 &0.67 & 0.1963 &-247.5 &246.8 &2.0 &-3.8 &3.8 &3.0 &-6.5 &5.5 &2.6 \\
BPII-1 &15.63 &1.33 & 0.1963 &-494.3 &493.7 &2.5 &-5.5 &-5.5 &4.0 &\bf{-10.9} &\bf{8.7} &\bf{3.9} \\
BPII-1 &15.63 &1.33 & -0.1963 &-494.3 &493.7 &2.5 &-5.5 &5.5 &4.0 &\bf{-8.7} &\bf{10.9} &\bf{3.9} \\
BPII-1 &31.25 &2.66 & 0.1963 &-987.5 &987.1 &3.5 &-6.9 &6.9 &5.1 &-17.7 &13.1 &5.0 \\
BPII-1 &39.06 &3.33 & 0.1963 &1233.9 &1233.6 &3.7 &-6.9 &6.9 &5.1 &-20.0 &14.5 &5.2 \\
\hline
GJT (BPII-2)&46.87 &4.00 & 0.1963 &-1479.8 &1477.0 &- &- &- &- &-10.0 &9.6  &- \\
GJT (BPII-2)&54.69 &4.67 & 0.1963 &-1720.5 &1720.8 &- &- &- &- &-11.5 &11.2 &- \\
GJT (BPII-2)&62.5 &5.33 & 0.1963  &-1966.7 &1966.2 &- &- &- &- &-13.3 &12.7 &- \\
GJT (BPII-2)&78.13 &6.01 & 0.1963 &-2458.3 &2457.8 &- &- &- &- &-16.9 &15.7 &- \\
GJT (BPII-2)&93.75 &8.00 & 0.1963 &-2949.7 &2949.7 &- &- &- &- &-20.3 &18.4 &- \\
GJT (BPII-2)&125.0 &10.66 &0.1963 &-3932.8 &3932.8 &- &- &- &- &-26.6 &22.4 &- \\
\hline
FAN &187.5 &16.00 & 0.1963 &-5906.2  &5906.2 &- &-  &-  &-  &-0.6 &0.4 &- \\
FAN &250.0 &21.33 & 0.1963 &-7874.9  &7874.9 &- &-  &-  &-  &-0.5 &0.3 &- \\
\hline
\end{tabular}
\caption{Minima, maxima and standard deviation of time-averaged velocity components 
for BPI ($\tau=-0.5, \kappa=1.0$) and BPII ($\tau=-0.5, \kappa=2.0$) in steady 
shear flow. All velocity values are given in $10^{-5}$ lattice units. The transient dynamics 
has not been included in the averages. The regimes comprise the formation
of an amorphous network (BPI-1), periodically recurring conformations (BPI-2 and BPII-1), 
two-dimensional double twist rolls (BPI-3), a one-dimensional travelling helical wave (BPII-2), 
a cholesteric helix oriented along the gradient direction (CHG), 
and a flow-aligned nematic state (FAN).
(Last six columns refer to the secondary flow.)}
\label{tab1}
\end{table*}
